\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
fixes in the graph processing section

\title{Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms}

@@

%\textbf{Orders induced by a graph.}
A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $v_1 \preceq_g v_2$ iff there is a path from $v_1$ to $v_2$ and there is no path from $v_2$ to $v_1$.
%Let $\opn{TOs}\left( g \right)$ be the set of total orders $o$ such that $\preceq_g \subseteq o$.
For example, $\preceq_h = \aset{\left( c_1,c_3 \right)}$. % and $\opn{TOs}\left( h \right)$ is the set of all permutations of $\aseq{c_1,c_2,c_3,c_4}$ in which $c_1$ comes before $c_3$.
%\textbf{Equivalence relation induced by a graph.}
A directed graph $g$ \emph{induces an equivalence relation} $\sim_g$ on its vertices defined such that $v_1 \sim_g v_2$ iff $v_1$ and $v_2$ belong to the same strongly connected component.
%\textbf{Linearizations of a dependency graph.}
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every pair of vertices $v_1,v_2\in V\left( g \right)$, $v_1 \preceq_g v_2$ implies $v_1 \ll v_2$, and if $v_1 \sim_g v_2$ and $\left( v_1,v_2 \right)\in f\left( \left[ v_1 \right] \right)$ hold then $v_1 \ll v_2$.
%\textbf{Partial order on graphs.}
We now define a partial order on graphs. If $g_1$ and $g_2$ are two graphs, then we write $g_1 \leq g_2$ iff $V\left( g_1 \right)\subseteq V\left( g_2 \right)$, and if $v\in V\left( g_1 \right)$, $e\in E\left( g_2 \right)$, and $v$ is an endpoint of $e$, then $e\in E\left( g_1 \right)$. 
For example, consider the graphs $h'$ and $h''$ such that $V\left( h' \right)=\aset{c_1,c_2,c_4}$, $E\left( h' \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right)}$, $V\left( h'' \right)=\aset{c_1,c_3,c_4}$, and $E\left( h'' \right)=\aset{\left( c_1,c_3 \right)}$. We have that $h'\leq h$, but $ h''\not\leq h$.

>>>>

\title{\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms}

@@

%\textbf{Orders induced by a graph.}
A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $v_1 \preceq_g v_2$ iff there is a path from $v_1$ to $v_2$ and there is no path from $v_2$ to $v_1$.
%Let $\opn{TOs}\left( g \right)$ be the set of total orders $o$ such that $\preceq_g \subseteq o$.
For example, $\preceq_h = \aset{\left( c_1,c_3 \right)}$. % and $\opn{TOs}\left( h \right)$ is the set of all permutations of $\aseq{c_1,c_2,c_3,c_4}$ in which $c_1$ comes before $c_3$.
%\textbf{Equivalence relation induced by a graph.}
A directed graph $g$ \emph{induces an equivalence relation} $\sim_g$ on its vertices defined such that $v_1 \sim_g v_2$ iff $v_1$ and $v_2$ belong to the same strongly connected component. We write $\left[ v \right]_g$ for the equivalence class of $v$ under $\sim_g$.
%\textbf{Linearizations of a dependency graph.}
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every pair of vertices $v_1,v_2\in V\left( g \right)$, $v_1 \preceq_g v_2$ implies $v_1 \ll v_2$, and if $v_1 \sim_g v_2$ and $ v_1 <_{\left[ v_1 \right]} v_2$ hold then $v_1 \ll v_2$.
%\textbf{Partial order on graphs.}

We now define a partial order on graphs. If $g_1$ and $g_2$ are two graphs, then we write $g_1 \leq g_2$ iff $V\left( g_1 \right)\subseteq V\left( g_2 \right)$, and if $v\in V\left( g_1 \right)$, $e\in E\left( g_2 \right)$, and $v$ is an endpoint of $e$, then $e\in E\left( g_1 \right)$. 
For example, consider the graphs $h'$ and $h''$ such that $V\left( h' \right)=\aset{c_1,c_2,c_4}$, $E\left( h' \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right)}$, $V\left( h'' \right)=\aset{c_1,c_3,c_4}$, and $E\left( h'' \right)=\aset{\left( c_1,c_3 \right)}$. We have that $h'\leq h$, but $ h''\not\leq h$.
